Efficient Handling of String-Number Conversion

### 2019-11-21 draft.tex

The domain restriction is formally defined by restricting the domain of each string variable by a chosen PFA. 
%
Namely, assuming that $X$ is the set of string variables of $\insc$,
a \emph{flat domain restriction} for $\insc$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$. 
%
We require that these PFA operate over pairwise disjoint sets of character variables. 
%
The particular choice of a PFA 
for each variable  depends on the strategy used in the implementation, and will be discussed in Section~\ref{section:implementation}.
%
The flattening $\outlf$ will be  built inductively to the structure of $\insc$.
Namely, in the following subsections we show how to build a flattening $\underf R {\phi}$ for every atomic string constraint $\phi$, 
and for a conjunction of string constraints, we let $\underf R {\phi \land \phi'} \defeq \underf R {\phi} \land \underf R {\phi'}$.
We then let $\outlf \defeq \underf R \insc$

@@

To formalise this correctness argument, we define an additional notation.
For an interpretation $I$ of string variables, 
we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$ of interpretations of $V_R\cup \#V_R$, containing combinations of interpretations of character variables of each $R(x)$ that encode the $I$.
%
Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
%
then its $R$-encoding is defined as the set $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$. That is, the interpretation of string variables is encoded and the interpretation of integer variables is kept as is.
%
We lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
%
The inductive argument needed in the proof of the correctness of the under-approximation then reads as
$$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
%
In the next sections, 
we will formulate the corresponding correctness lemma for flattenings constructed from each type of atomic string constraints.
%
We note that the restriction of the semantics of $\underf R \phi$ here is needed since $\underf R \phi$ will be constructed with some auxiliary variables.

>>>>

The domain restriction is formally defined by restricting the domain of each string variable by a chosen PFA. 
%
Namely, assuming that $X$ is the set of string variables of $\insc$,
a \emph{flat domain restriction} for $\insc$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$ \changed{over character variables $V_x$.}
string %
We require that these PFA operate over pairwise disjoint sets of character variables\changed{, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.}
%
The particular choice of a PFA 
for each variable  depends on the strategy used in the implementation, and will be discussed in Section~\ref{section:implementation}.
%
The flattening $\outlf$ will be  built inductively to the structure of $\insc$.
Namely, in the following subsections we show how to build a flattening $\underf R {\phi}$ for every atomic string constraint $\phi$, 
and for a conjunction of string constraints, we let $\underf R {\phi \land \phi'} \defeq \underf R {\phi} \land \underf R {\phi'}$.
We then let $\outlf \defeq \underf R \insc$

@@

To formalise this correctness argument, we define an additional notation.
For an interpretation $I$ of string variables, 
we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$ of interpretations of $V_R\cup \#V_R$, containing combinations of interpretations of character variables of each $R(x)$ that encode the $I$.
%
\changed{
Further, we define an $R$-encoding for an interpretation $I \cup I'$ of a general string constraint, consiting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables.
%
An $R$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding where $e\in \encode R(I)$ and the original integer interpretation $I'$ which satisfies that for every string leght variable $|x|$ in the domain of $I'$,
$|x| = \sum_{v\in V_x,I(v)\neq\epsilon}\#v$. 
That is, the interpretation of string variables is encoded as usual, the interpretation of integer variables is kept as is, 
and for each string legth variable $|x|$ in the domain of $I'$, 
the value of $|x|$ is consistent with the encoding of $x$ by variables $V_x$ and $\#V_x$.
The set of all $R$-encodings of $(I\cup I')$ is then denoted $\encode R {(I\cup I')}$}
%
%Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
%%
%then an $R$-encoding of $I \cup I'$ is any interpretation $e \cup I$ with  $e:V_R \cup \#V_R \cup \Simga_\epsilon$ 
%such that $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$. That is, the interpretation of string variables is encoded and the interpretation of integer variables is kept as is.
%
%
and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
%
The inductive argument needed in the proof of the correctness of the under-approximation then reads as
$$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
%
In the next sections, 
we will formulate the corresponding correctness lemma for flattenings constructed from each type of atomic string constraints.
%
We note that the restriction of the semantics of $\underf R \phi$ here is needed since $\underf R \phi$ will be constructed with some auxiliary variables.
